---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# fastnum: Collection of fast numerical computation tools in R

<!-- badges: start -->
<!-- badges: end -->

`{fastnum}` is a collection of tools and functions for numerical computation and scientific computing using C++ at its core. This includes probability distributions, generation of random numbers, and tools for functional programming. This is still an R package, not CRAN-style, rather a module that must be accessed through `{box}` R package. 

## Installation

You need to install `carrier` first. See the [installation guide](https://joshuamarie.com/carrier/installation.html) for the details. 

The package has no pre-built binaries yet, so the installation of `fastnum` has to be built from scratch. 

``` bash
carrier install gh:joshuamarie/fastnum-module --install-deps
```

## Usage

You can't use `fastnum` by loading it through `library()` or `::`, you need `{box}` R package. Currently, the current version of `{box}` cannot import `fastnum` being managed by `carrier`, you have to install the patched forked version of `{box}` (see [details](https://joshuamarie.com/carrier/installation.html#the-box-fork)). 

```{r}
box::use(fastnum)
```

### Standard Math Module

`fastnum` has collection of mathematical functions, some were imported from the base R itself. 

```{r}
fastnum$square(5)
```

### Random Number Generation

By default, `fastnum`'s submodule `random` contains the function to generate random numbers

```{r}
fastnum$random$draw$normal(10L)
```



