---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# statmodule: Collection of statistical methods in R

<!-- badges: start -->
<!-- badges: end -->

`{statmodule}` is a collection of tools and functions for numerical computation, scientific computing, and statisticial methods in R using C++ at its core. This includes probability distributions, generation of random numbers, and tools for functional programming. This is still an R package, not CRAN-style, rather a module that must be accessed through `{box}` R package. 

## Installation

You need to install `{carrier}` first. See the [installation guide](https://joshuamarie.com/carrier/installation.html) for the details. 

The package has no pre-built binaries yet, so the installation of `{statmodule}` has to be built from scratch. 

``` bash
carrier install gh:joshuamarie/stat-box-module --install-deps
```

## Usage

You can't use `{statmodule}` by attaching it through `library()` or `::`, you need `{box}` R package. Currently, the current version of `{box}` cannot import `{statmodule}` being managed by `carrier`, you have to install the patched forked version of `{box}` (see [details](https://joshuamarie.com/carrier/installation.html#the-box-fork)). 

```{r}
box::use(sm = statmodule)
```

### Standard Math Module

`{statmodule}` has collection of mathematical functions, some were imported from the base R itself. 

```{r}
sm$square(5)
```

### Random Number Generation

`{statmodule}`'s submodule `random` contains the function to generate random numbers. By default, it depends on Boost's probability distribution library and `{dqrng}`'s fast pseudo random number generator. 

```{r}
set.seed(123)
sm$random$draw$normal(10L)
```



